The language of generalization: Probability, vagueness, and interaction

### 2018-05-14 paper/case1-generics.Rmd
final pass case 1; refresh fig caps

Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propagation [@Rhodes2012], motivation [@Cimpian2007], and many other facets of everyday reasoning.
In addition, generics have been the case study of choice for the semantics of the language of generalization because of their tantalizing similarity to quantified statements (e.g., "Most dogs bark").
However, intuitions and empirical data argue that generics simply do not reduce to quantified statements [e.g., @Khemlani2012, @Prasada2013, @Cimpian2010].

We first investgate how the *underspecified threshold* endorsement model predicts actual human endorsements of generic statements.
We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions previously discussed in the empirical literature on generics [@Prasada2013]: characteristic features displayed by a majority (e.g., "Ducks have wings."),  characteristic features displayed by a minority (e.g., "Robins lay eggs."), features that are *striking* or *dangerous* (e.g. "Mosquitos carry malaria."),  noncharacteristic features displayed by a minority (e.g., "Robins are female."), and features that are totally absent (e.g. "Lions lay eggs.").
We further craft sentences with the goal of eliciting the full range of acceptability judgments (intuitively: "true", "false", and "indeterminate") for generics with properties of low, medium, and high referent-prevalence (Expt. 1a).
We examine generics about animal categories in order to reliably measure the prior belief distribution over the prevalence of features $P(p)$.
The prevalence elicitation procedure (Expt. 1b) includes measurements of the referent-category feature-probabilities $p$  (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to generate predictions for the endorsement model (Eq. \ref{eq:S1}) as well as for simpler, alternative models.

@@

Participants were shown thirty generic sentences in a randomized order.
They were asked to press one of two buttons (randomized between-participants) to signify whether they agreed or disagreed with the sentence (see Table 2 in Appendix for complete list). 
The thirty sentences were presented in a random order between participants and covered a range of conceptual categories described above.
Approximately 10 true, 10 false, and 10 uncertain truth-value generics were selected.
All 30 generic sentences are shown in Figure\ \@ref(fig:generics-endorsement-figure)A.
As an attention check, participants were asked at the end of the trials which button corresponded to "Agree".
4 participants were excluded for failing this trial.

@@

In addition to these categorical differences between our thirty generic statements, we find a continuum of endorsement values (Figure\ \@ref(fig:generics-endorsement-figure)A).
Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, rejected completely, and all shades in between.
We next measure the prevalence prior distribution and use them to articulate a set of quantitative models that try to predict these endorsement data.

@@

The prevalence prior $P(p)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g., \textsc{lays eggs}) across relevant categories. 
To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon). 
Ask yourself "is it female?" 
Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%). 
Now, do you think it lays eggs? 
Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young. 
That is, the answer is roughly either 50\% or 0\% depending on the kind of creature you are thinking of^[
  The subjective probability may, in fact, be non-zero and small as opposed to 0. 
  Non-zero probabilities allow for the intuitive possibility of a dog that lays eggs potentially due to some strange   generic mutation or the interaction of dog genetics with a strange environment. 
].

This thought experiment decomposes the prevalence prior $P(p)$ into a prior distribution on kinds $P(k)$ and then a conditional probability of the prevalence given the kind $P(p \mid k)$.
We will use this decomposition to measure the prevalence prior $P(p) = \int_{k} P(p \mid k) \diff k$ and perform Bayesian data analysis to accurately reconstruct the prevalence prior.
We measured prior distributions empirically for the set of properties (e.g., *lays eggs, carries malaria*; 21 in total) used in our generic sentences in Expt. 1a.
To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").

@@

There is a lot of diversity in the shapes of the elicited prior distributions (8 examples shown in Figure\ \@ref(fig:generic-endorsement-priors-figure)A), which is roughly consistent with the schematic prior distributions used in the *Model Simulations* section (Figure\ \@ref(fig:simulations)A).
The property *being female* is present in almost all categories in almost exactly the same proportion, whereas properties such as *laying eggs* or *having spots* exhibit more structure represented by the multimodality of these distributions. 
*Being red* exists mostly at extremely low prevalence levels (i.e., 0 prevalence) but also at high prevalence levels (e.g., 50\% or 100\%), whereas *carrying malaria* is really only present at low prevalence levels.
This diversity is important because our endorsement model makes different predictions depending on the shape of the distrubution

@@

<!-- Accurately modeling the prior data is important to generate precise quantitative predictions about endorsement. -->
In order to integrate the results of this prior measurement task into our model of endorsement, we must accurately model the prior elicitation data.
We approximate the prevalence distribution for each property (e.g., \textsc{lay eggs}) with a Mixture of Betas model, which assumes that the data generated for each kind comes from one of two underlying Beta distributions.^[
  The Beta distribution is chosen because the support of this distribution is numerical values between 0 - 1, exactly the form of the response data in the prior elicitation task.
] 
We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in prevalence or prevalence values close to or equal to 0.^[
  This assumption is similar in spirit to that employed by *Hurdle Models* of epidemiological data, where the observed count of zeros is often substantially greater than one would expect from standard models, such as the Poisson [e.g., when modeling adverse reactions to vaccines; @hurdleModels]
]
This "null distribution" is potentially present for all features in exactly the same way (i.e., the lack of producing the feature).
The second distribution represents kinds of animals who *do have* such a mechanism, and the two parameters of this distribution are not specified *a priori* and are not the same for all properties, but are inferred on a property-wise basis from participants' responses.
The *Mixture of Betas* distribution has a third free parameter (for each property), the relative contribution of the "null distribution" (for example: we expect the "null distribution" to not contribute at all to properties like *being female*, for which almost all categories have at least some members with the property).
To ensure the *Mixture of Betas* model of the prior is not overly complex, we fit an additional model that represents only a single underlying distribution (*Single Beta*) for a comparison.
<!-- is flexible and can represent different shapes for different properties (e.g., the differences in prevalence judgments for \textsc{lay eggs} vs. \text{has wings}). -->
For more details about model implementation and inference, see Appendix C.

The prior distributions over prevalence are well modeled as a mixture of two Beta distributions and not as a single Beta distribution (Figure\  \@ref(fig:generic-endorsement-priors-figure)B; red vs. blue lines). 
The *Single Beta* model provides a good fit for the *being female* distribution, but overly smooths the other distributions, washing out the latent structure in participants' responses.
One property that the *mixture of Betas* model does not perfectly capture is the prior distribution over the feature *lays eggs*.
The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%; a simple two-component mixture model has no way to account for such a tri-modal distribution.^[
  The third mode at 100\% is not attributable to categories for which all members could be female (e.g., chickens). Instead, it appears that some participants are responding that 100\% of several different kinds of birds (e.g., robins) lay eggs. This may result from participants implicitly only considering female members of the category as relevant to answer a question about a reproductive capactiy like *lays eggs*; this restriction of what enters into the prevalence computation is known as *domain restriction* and has been observed in other prevalence elicitation tasks [e.g., @Prasada2013].
];
A more complex model (i.e., one with three mixture components) would be necessary to perfectly account for this item. 
Using a three-component model for this distribution does not change the resulting model predictions and we maintain the simpler two-component mixture for uniformity.

@@

We can now compute the predictions of our endorsement model; we first articulate a set of alternatives: models that have been previously-proposed in the literature, an alternative-form of our proposed endorsement model, and our full endorsement model.

@@

We present two baseline, quantitative models that have previously been used in the empirical literature on generic language.
In addition to serving as alternatives, these regressions model help us understand the statistical properties of our thirty items. 
First, we estimate how well referent prevalence itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
Second, we include *cue validity*---the probability of a kind given the feature---as a second predictor in a linear model.
We fit these models using standard maximum-likelihood techniques and model uncertainty in the input measurements (i.e., referent prevalence, cue validity) by bootstrapping those data.

@@

From the prevalence prior data (Expt. 1b), we estimate participants' beliefs about the referent prevalence (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}).
We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ \@ref(fig:generic-endorsement-priors-figure), upper-right: lower-left facet). 
Referent prevalence alone does okay at predicting these data because our stimulus set includes generics that are true with high prevalence properties (e.g., "Leopards have spots.") and false with low prevalence properties (e.g., "Leopards have wings.").

@@

A linear model that uses predictors for both referent-prevalence and cue validity does a better job at explaining the endorsement data than just prevalence alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
This model is able to account for the endorsements of examples like "Mosquitos carry malaria" (model endorsement and bootstrapped-95\% confidence interval = `r round(reg.mosquitos.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.carry[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.mosquitos.carry[[1,"prediction_ci_upper"]], 2)`]) and "Lions have manes" (`r round(reg.lions.manes[[1,"prediction_mean"]], 2)` [`r round(reg.lions.manes[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.lions.manes[[1,"prediction_ci_upper"]], 2)`])), as these features are very diagnostic of the kind (human endorsement both $> 0.9$).
Deviations, however, still remain.
For example, "Robins lay eggs" still receives only intermediate endorsement by this model (`r round(reg.robins.lay.eggs[[1,"prediction_mean"]], 2)` [`r round(reg.robins.lay.eggs[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.robins.lay.eggs[[1,"prediction_ci_upper"]], 2)`]; human endorsement = `r round(reg.robins.lay.eggs[[1,"MAP_h"]], 2)` [`r round(reg.robins.lay.eggs[[1,"low"]], 2)`,
`r round(reg.robins.lay.eggs[[1,"high"]], 2)`]), and "Mosquitos don't carry malaria" is judged to be a pretty good statement (`r round(reg.mosquitos.dont.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.mosquitos.dont.carry[[1,"prediction_ci_upper"]], 2)`]; human endorsement = `r round(reg.mosquitos.dont.carry[[1,"MAP_h"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"low"]], 2)`,
`r round(reg.mosquitos.dont.carry[[1,"high"]], 2)`]).

"Robins lay eggs" and "Mosquitos don't carry malaria" highlight a shortcoming of reducing structured prevalence prior distributions to single point-estimates of cue validity.
"Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for a particular kind of bird like "Robins".
Thus, the cue validity is low even though robins are in the distinctive part of the "lays eggs" prevalence prior distribution (e.g., Figure\ \@ref(fig:simulations)A bottom).
Furthermore, cue validity glosses over the difference between "undiagnostic" features (features present in almost every category; e.g., "not carrying malaria") and "false" features (features that are absent a particular category; e.g., "lions" and "lay eggs"; see Appendix B for more discussion of this distinction).
Such a model makes the wrong prediction for non-distinctive properties with high referent prevalence (e.g., "Mosquitos don't carry malaria").
A simple metric like cue validity is too blunt to capture these subtleties.

@@

<!-- The model we propose for endorsing generalizations is a model of an agent that decides whether or not to say the generalization to a naive interpreter. -->
For each of these communicative endorsement models, we build a joint Bayesian data analysis model of the referent-category prevalence $p$, prevalence priors $P(p)$ (both from Expt. 1b data), and the endorsement data (Expt. 1a). 
Empirically elicited referent prevalence and prevalence prior data (Expt. 1b) directly constrain their corresponding parameters in the model ($p$ in Eq. \ref{eq:S1} and $P(p)$ in Eq. \ref{eq:L0}, respectively). 
The prevalence prior $P(p)$ is modeled as a mixture of Betas while referent prevalence is modeled by a single Beta distribution.
The endorsement data (Expt. 1a) is modeled by our endorsement model (Eq. \ref{eq:S1}), which has one free parameter $\lambda$.
Modeling the data from both Expt. 1a and 1b by a single, joint-inference model simultaneously makes explicit our assumptions about how these data were generated and is the proper way to represent the uncertainty in our measurement of the prior elicitation data (see Appendix C and Figure\ \@ref(fig:genericsModelDiagram) for further model specification details).
To learn about the credible values of the parameters of the joint-inference model and resulting model predictions, we ran an incrementalized version of MCMC [@Ritchie2016] for 3 chains of 150,000 iterations, discarding the first 50,000 for burn-in.

@@

To provide a strong alternative model, we lesion our uncertain threshold model so that it has a fixed threshold $\theta$.
In addition, we make this fixed-threshold a parameter of the data-analysis model, to search for the best possible fixed-threshold. 
Finally, a fixed-threshold model will have to accommodate responses that are literally inconsistent with the threshold (i.e., a participant endorsing a generic when the referent prevalence is less than $\theta$); we thus outfit this model with an additional noise parameter, to allow for random guessing. 
Thus, our fixed-threshold alternative model says that participants make an information-theoretic decision, taking into account the interpreter's prior distribution $P(p)$, using a fixed-threshold semantics, where deviations from a pure information-theoretic decision are accounted for by noise.
This alternative model has 2 additional parameters to our uncertain threshold model (the fixed-threshold and the proportion of noise responses).
<!-- We examine the predictions of this alternative model first. -->

@@

```{r generics-endorsement-figure, fig.width = 11, fig.height=8.5, fig.cap="Endorsing generalizations about categories. Top left: Human elicited endorsements for thirty generic sentences reveal a continuuum of endorsements. Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent prevalence alone (lower left) and prevalence + cue validity (lower right). Bottom: Five example prevalence priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the referent prevalence. These distributions are inferred using all three data sources from Expt. 1 (see Figure \\ref{fig:genericsModelDiagram} for an overview of the Bayesian data analytic approach).", cache = F}

@@

Generic language is the premier case study for generalizations in language. 
Generics have been studied extensively in the cognitive and developmental psychological literatures and shown to have deep implications for wide ranging phenomena from stereotype propagation [@Rhodes2012] to motivation [@Cimpian2007].
Heretofore, no formal model has been able to pass the most basic truth-functional tests of the semantics of generics: knowing when they are true and false.
<!-- Determining the truth conditions is the first step towards articulating a formal theory of how the language updates beliefs. -->
This empirical case study demonstrates that a semantics based on the prevalence of the feature is tenable despite of alleged counterexamples (e.g., "Robins lay eggs" vs. "Robins are female").
The key theoretical insight is that the truth-functional semantics is underspecified, or vague, and resolved in context by a process of probabiistic inference.
Our model provides a clear delineation of world knowledge (formalized as a prevalence prior) from the semantics of generics. 
We return to this point, and its implications for theory-building, in the general discussion.

>>>>

Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") are of substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propagation [@Rhodes2012], motivation [@Cimpian2007], and many other facets of everyday reasoning.
In addition, generics have been the case study of choice for the semantics of the language of generalization because of their tantalizing similarity to quantified statements (e.g., "Most dogs bark").
However, intuitions and empirical data argue that generics simply do not reduce to quantified statements in a simple way [e.g., @Khemlani2012; @Prasada2013; @Cimpian2010].

We first investgate how the *underspecified threshold* endorsement model predicts actual human endorsements of generic statements.
We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions previously discussed in the empirical literature on generics [@Prasada2013]: characteristic features displayed by a majority (e.g., "Ducks have wings."),  characteristic features displayed by a minority (e.g., "Robins lay eggs."), features that are *striking* or *dangerous* (e.g. "Mosquitos carry malaria."),  noncharacteristic features displayed by a minority (e.g., "Robins are female."), and features that are totally absent (e.g. "Lions lay eggs.").
We further craft sentences with the goal of eliciting the full range of acceptability judgments (intuitively: "true", "false", and "indeterminate") for generics with properties of low, medium, and high referent-prevalence (Expt. 1a).
We examine generics about animal categories in order to reliably measure the prior belief distribution over the prevalence of features $P(p)$.
The prevalence elicitation procedure (Expt. 1b) includes measurements of the referent-prevalence $p$ for different categories  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to generate predictions for the endorsement model (Eq. \ref{eq:S1}) as well as for simpler, alternative models.

@@

Participants were shown thirty generic sentences in a randomized order.
They were asked to press one of two buttons (randomized between-participants) to signify whether they agreed or disagreed with the sentence (see Figure\ \@ref(fig:generics-endorsement-figure)A for the full list). 
The thirty sentences were presented in a random order between participants and covered a range of conceptual categories described above.
Approximately ten true, ten false, and ten uncertain truth-value generics were selected.
As an attention check, participants were asked at the end of the trials which button corresponded to "Agree".
Four participants were excluded for failing this trial.

@@

In addition to these categorical differences between our thirty generic statements, we find a continuum of endorsement values (Figure\ \@ref(fig:generics-endorsement-figure)A).
Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, rejected completely, and all shades in between.
We next measure the prevalence prior distribution and use them to articulate a set of quantitative models that try to predict this quantitative variability in endorsements.

@@

The prevalence prior $P(p)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g., \textsc{lays eggs}) across relevant categories. 
To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon). 
Ask yourself "is it female?" 
Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%). 
Now, do you think it lays eggs? 
Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young. 
That is, the answer is roughly either 50\% or 0\% depending on the kind of creature you are thinking of.^[
  The subjective probability may, in fact, be non-zero and small as opposed to 0. 
  Non-zero probabilities allow for the intuitive possibility of a mammal animal that generally reproduces by giving live birth which in fact lays eggs, potentially explained by some strange generic mutation.
]

This thought experiment decomposes the prevalence prior $P(p)$ into a prior distribution on kinds $P(k)$ and then a conditional probability of the prevalence given the kind $P(p \mid k)$.
We will use this decomposition to measure the prevalence prior $P(p) = \int_{k} P(p \mid k) \diff k$ and build a structured statistical model to accurately reconstruct the prevalence prior.
We measured prior distributions empirically for the set of properties (e.g., *lays eggs, carries malaria*; 21 in total) used in our generic sentences in Expt. 1a.
To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").

@@

The elicited prior distributions have a diversity of shapes (8 examples shown in Figure\ \@ref(fig:generic-endorsement-priors-figure)A) that are roughly consistent with the schematic prior distributions used in the *Model Simulations* section (Figure\ \@ref(fig:simulations)A).
The property *being female* is present in almost all categories in almost exactly the same proportion, whereas properties such as *laying eggs* or *having spots* exhibit more structure represented by the multimodality of these distributions. 
*Being red* exists mostly at extremely low prevalence levels (i.e., 0 prevalence) but also at high prevalence levels (e.g., 50\% or 100\%), whereas *carrying malaria* is really only present at low prevalence levels.
This diversity is important because our endorsement model makes different predictions depending on the shape of the distrubution.

@@

<!-- Accurately modeling the prior data is important to generate precise quantitative predictions about endorsement. -->
In order to integrate the results of this prior measurement task into our model of endorsement, we must build a statistical model of the prior elicitation data.
We approximate the prevalence distribution for each property (e.g., \textsc{lay eggs}) with a Mixture of Betas model, which assumes that the data generated for each kind comes from one of two underlying Beta distributions.^[
  The Beta distribution is chosen because the support of this distribution is numerical values between 0 - 1, exactly the form of the response data in the prior elicitation task.
] 
We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in prevalence or prevalence values close to or equal to 0.^[
  This assumption is similar in spirit to that employed by *Hurdle Models* of epidemiological data, where the observed count of zeros is often substantially greater than one would expect from standard models, such as the Poisson [e.g., when modeling adverse reactions to vaccines; @hurdleModels]
]
This "null distribution" is potentially present for all features in exactly the same way (i.e., the lack of producing the feature).
The second distribution represents kinds of animals who *do have* such a mechanism, and the two parameters of this distribution are not specified *a priori* and are not the same for all properties, but are inferred on a property-wise basis from participants' responses.
The *Mixture of Betas* distribution has a third free parameter (for each property), the relative contribution of the "null distribution" (for example: we expect the "null distribution" to not contribute at all to properties like *being female*, for which almost all categories have at least some members with the property).
To ensure the *Mixture of Betas* model of the prior is not overly complex, we fit an additional model that represents only a single underlying distribution (*Single Beta*) for a comparison.
<!-- is flexible and can represent different shapes for different properties (e.g., the differences in prevalence judgments for \textsc{lay eggs} vs. \text{has wings}). -->
For more details about model implementation and inference, see Appendix C.

The prior distributions over prevalence are well modeled as a mixture of two Beta distributions and not as a single Beta distribution (Figure\  \@ref(fig:generic-endorsement-priors-figure)B; red vs. blue lines). 
The *Single Beta* model provides a good fit for the *being female* distribution, but overly smooths the other distributions, washing out the latent structure in participants' responses.
One property that the *mixture of Betas* model does not perfectly capture is the prior distribution over the feature *lays eggs*.
The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%; a simple two-component mixture model has no way to account for such a tri-modal distribution.^[
  The third mode at 100\% is not attributable to categories for which all members could be female (e.g., chickens). Instead, it appears that some participants are responding that 100\% of several different kinds of birds (e.g., robins) lay eggs. This may result from participants implicitly only considering female members of the category as relevant to answer a question about a reproductive capactiy like *lays eggs*; this restriction of what enters into the prevalence computation is known as *domain restriction*, is posited in several theories of generics [e.g., @Cohen1999], and has been observed in other prevalence elicitation tasks [e.g., @Prasada2013].
]
A more complex model (i.e., one with three mixture components) would be necessary to perfectly account for this item. 
Using a three-component model for this distribution does not change the resulting model predictions and we maintain the simpler two-component mixture for uniformity.

@@

We can now compute the predictions of our endorsement model; we first articulate a set of alternatives: models that have been previously proposed in the literature, an alternative form of our proposed endorsement model, and our full endorsement model.

@@

We present two baseline, quantitative models that have previously been used in the empirical literature on generic language.
In addition to serving as alternatives, these regressions model help us understand the statistical properties of our thirty items. 
First, we estimate how well referent prevalence itself predicts generic endorsement (e.g., does the fraction of robins that lay eggs predict the felicity of *Robins lay eggs*?).
Second, we include *cue validity*---the probability of a kind given the feature---as a second predictor in a linear model.
We fit these models using standard maximum-likelihood techniques and model uncertainty in the input measurements (i.e., referent prevalence, cue validity) by bootstrapping those data.

@@

From the prevalence prior data (Expt. 1b), we estimate participants' beliefs about the referent prevalence (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}) and use it to predict endorsement.
We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ \@ref(fig:generic-endorsement-priors-figure), upper-right: lower-left facet). 
Referent prevalence alone does okay at predicting these data because our stimulus set includes generics that are true with high prevalence properties (e.g., "Leopards have spots.") and false with low prevalence properties (e.g., "Leopards have wings.").

@@

A linear model that uses predictors for both referent-prevalence and cue validity does a better job at explaining the endorsement data than just prevalence alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
This model is able to account for the endorsements of examples like "Mosquitos carry malaria" (model endorsement and bootstrapped-95\% confidence interval = `r round(reg.mosquitos.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.carry[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.mosquitos.carry[[1,"prediction_ci_upper"]], 2)`]) and "Lions have manes" (`r round(reg.lions.manes[[1,"prediction_mean"]], 2)` [`r round(reg.lions.manes[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.lions.manes[[1,"prediction_ci_upper"]], 2)`])), as these features are very diagnostic of the kind (human endorsement both $> 0.9$).
Deviations, however, still remain.
For example, "Robins lay eggs" still receives only intermediate endorsement by this model (`r round(reg.robins.lay.eggs[[1,"prediction_mean"]], 2)` [`r round(reg.robins.lay.eggs[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.robins.lay.eggs[[1,"prediction_ci_upper"]], 2)`]; human endorsement = `r round(reg.robins.lay.eggs[[1,"MAP_h"]], 2)` [`r round(reg.robins.lay.eggs[[1,"low"]], 2)`,
`r round(reg.robins.lay.eggs[[1,"high"]], 2)`]), and "Mosquitos don't carry malaria" is misjudged to be a pretty good statement (`r round(reg.mosquitos.dont.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.mosquitos.dont.carry[[1,"prediction_ci_upper"]], 2)`]; human endorsement = `r round(reg.mosquitos.dont.carry[[1,"MAP_h"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"low"]], 2)`,
`r round(reg.mosquitos.dont.carry[[1,"high"]], 2)`]).

"Robins lay eggs" and "Mosquitos don't carry malaria" highlight a shortcoming of reducing structured prevalence prior distributions to single point-estimates of cue validity.
*Lays eggs* is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for a particular kind of bird like *robins*.
Thus, the cue validity is low even though robins are in the distinctive part of the "lays eggs" prevalence prior distribution (Figure\ \@ref(fig:simulations)A bottom).
Furthermore, cue validity glosses over the difference between "undiagnostic" features (features present in almost every category; e.g., "not carrying malaria") and "false" features (features that are absent a particular category; e.g., "lions" and "lay eggs"; see Appendix B for more discussion of this distinction).
Such a model makes the wrong prediction for non-distinctive properties with high referent prevalence (e.g., "Mosquitos don't carry malaria").
A simple metric like cue validity is too blunt to capture these subtleties.

@@

<!-- The model we propose for endorsing generalizations is a model of an agent that decides whether or not to say the generalization to a naive interpreter. -->
For each of these communicative endorsement models, we build a joint Bayesian data analysis model of the referent prevalence $p$, prevalence priors $P(p)$ (both from Expt. 1b data), and the endorsement data (Expt. 1a). 
Empirically elicited referent prevalence and prevalence prior data (Expt. 1b) directly constrain the parameters that generate those quantities in the model ($p$ in Eq. \ref{eq:S1} and $P(p)$ in Eq. \ref{eq:L0}, respectively). 
The prevalence prior $P(p)$ is modeled as a mixture of Betas while referent prevalence is modeled by a single Beta distribution.
The endorsement data (Expt. 1a) is modeled by our endorsement model (Eq. \ref{eq:S1}), which has one free parameter $\lambda$.
Predicting the data from both Expt. 1a and 1b by a single, joint-inference model simultaneously makes explicit our assumptions about how these data were generated and is the proper way to represent the uncertainty in our measurement of the prior elicitation data (see Appendix C and Figure\ \@ref(fig:genericsModelDiagram) for further model specification details).
To learn about the credible values of the parameters of the joint-inference model and resulting model predictions, we ran an incrementalized version of MCMC [@Ritchie2016] for 3 chains of 150,000 iterations, discarding the first 50,000 for burn-in.

@@

For a strong alternative model, we lesion our uncertain threshold model so that it has a fixed threshold $\theta$.
In addition, we make this fixed-threshold a parameter of the data-analysis model, to search for the best possible fixed-threshold. 
Finally, a fixed-threshold model will have to accommodate responses that are literally inconsistent with the threshold (i.e., a participant endorsing a generic when the referent prevalence is less than $\theta$); we thus outfit this model with an additional noise parameter, to allow for random guessing. 
Thus, our fixed-threshold alternative model says that participants make an information-theoretic decision, taking into account the interpreter's prior distribution $P(p)$, using a fixed-threshold semantics, where deviations from a pure information-theoretic decision are accounted for by noise.
This alternative model has 2 additional parameters to our uncertain threshold model (the fixed-threshold and the proportion of noise responses).
<!-- We examine the predictions of this alternative model first. -->

@@

```{r generics-endorsement-figure, fig.width = 11, fig.height=8.5, fig.cap="Endorsing generalizations about categories. A: Human elicited endorsements for thirty generic sentences reveal a continuum of endorsements. B: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent prevalence alone (lower left) and prevalence + cue validity (lower right). C: Five example prevalence priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the referent prevalence. These distributions are inferred using all three data sources from Expt. 1 (see Figure \\ref{fig:genericsModelDiagram} for an overview of the Bayesian data analytic approach).", cache = F}

@@

Generic language is the premier case study for generalizations in language. 
Generics have been studied extensively in the cognitive and developmental psychological literatures and have deep implications for wide ranging phenomena from stereotype propagation [@Rhodes2012] to motivation [@Cimpian2007].
Heretofore, no formal model has been able to pass the most basic truth-functional tests of the semantics of generics: knowing when they are true and false.
<!-- Determining the truth conditions is the first step towards articulating a formal theory of how the language updates beliefs. -->
This empirical case study demonstrates that a semantics based on the prevalence of the feature is tenable despite of alleged counterexamples (e.g., "Robins lay eggs" vs. "Robins are female").
The key theoretical insight is that the truth-functional semantics is underspecified, or vague, and resolved in context by a process of probabilistic inference.
Our model provides a clear delineation of world knowledge (formalized as a prevalence prior) from the semantics of generics. 
We return to this point, and its implications for theory-building, in the general discussion.

### 2018-05-14 paper/comgen-paper.Rmd
final pass case 1; refresh fig caps

```{r uniformPriorSimulation, fig.cap = "Computational model behavior assuming a uniform prior over prevalence. A: Interpretation model posteriors assuming different fixed thresholds. High thresholds rule out more world-states (prevalence levels), leaving fewer world-states among which to distribute the full probability mass. B: Full interpretation model marginalizes over possible thresholds to return a posterior distribution that favors higher prevalence levels in a graded manner. C: Endorsement model predicts higher rates of endorsemens as prevalence levels increase.", fig.width = 13, fig.asp = 0.3, out.width = "100%", fig.align = "center", cache = F}

@@

```{r simulations, fig.cap = "Model simulations assuming different prevalence priors. Top: Prior distributions over the prevalence of a feature for 6 example features. Shapes of the priors were chosen to intuitively correspond to the properties labeling the distributions. Arrows show intuitive referent-category prevalence for a target category. Bottom: The interpreter model posterior distributions over prevalence upon hearing a generalization about a novel category. Numbers at bottom correspond to endorsement model predictions for endorsing the generalization for  the referent-category whose prevalence is shown in the top facets (e.g., \"Mosquitos carry malaria\").", fig.width = 9, fig.asp = 0.37, out.width = "100%", fig.align = "center", cache=F}

>>>>

```{r uniformPriorSimulation, fig.cap = "Computational model behavior assuming a uniform prior over prevalence. A: Interpretation model posteriors assuming different fixed thresholds (facets). High thresholds rule out more world-states (prevalence levels), leaving fewer world-states among which to distribute the full probability mass. B: Generic interpretation model averages over all thresholds to return a posterior distribution that favors higher prevalence levels in a graded manner. C: Endorsement model predicts higher rates of endorsemens as prevalence levels increase.", fig.width = 13, fig.asp = 0.3, out.width = "100%", fig.align = "center", cache = F}

@@

```{r simulations, fig.cap = "Model simulations assuming different prevalence priors. Top: Prevalence priors for six example features. Shapes of the priors were chosen to intuitively correspond to the properties labeling the distributions. Arrows show referent-prevalence for a target category. Bottom: Interpretation model posterior distributions over prevalence upon hearing a generalization about a novel category. Numbers at bottom correspond to endorsement model predictions for endorsing the generalization for  the referent-category whose prevalence is shown in the top facets (e.g., \"Mosquitos carry malaria\").", fig.width = 9, fig.asp = 0.37, out.width = "100%", fig.align = "center", cache=F}
